\thispagestyle{empty}

\cleardoublepage        
\vspace*{1cm}  
\phantomsection
\addcontentsline{toc}{chapter}{Acknowledgement}
\begin{center}
 \Large {\bf \uppercase{Acknowledgement}}
\end{center}

\vspace{3\baselineskip}
\begin{justify}
\noindent
As a group, we extend our heartfelt gratitude to \textbf{Dr. Vaishali V. Ingale}, whose unwavering support, insightful guidance, and constructive feedback have been instrumental in the successful completion of this project. Her mentorship has truly enriched our learning experience and contributed significantly to the quality of our work. We are deeply thankful to \textbf{Dr. Vibha Vyas}, Head of the Department of Electronics and Telecommunications, for providing the necessary resources and facilities that facilitated the execution of this project. Moreover, we would like to express our appreciation to our friends and classmates for their understanding, patience and encouragement throughout this journey. Their unwavering support has been a constant source of strength and motivation. Lastly, we extend our gratitude to all the individuals who contributed to this project in various capacities, whether through internet resources or by providing valuable insights. Your collaboration and willingness to share expertise have enriched the outcome of our work. This project stands as a testament to the collective effort and collaboration of all those mentioned above. Thank you for being an integral part of our journey.
\end{justify}

\vspace{1.5\baselineskip}

\begin{center}
\begin{tabular}{lll}
\textbf{Name} & \textbf{Roll Number} & \textbf{Signature} \\[1em]
Tanvi Anil Deshmukh & 112107013 & \rule{4cm}{0.4pt} \\[1em]
Karan Rajkumar Doshi & 112107015 & \rule{4cm}{0.4pt} \\[1em]
Niranjan Pratapsinh Jadhav & 112107022 & \rule{4cm}{0.4pt} \\
\end{tabular}
\end{center}


\vspace{4\baselineskip}
\noindent
COEP Technological University, Pune \\
Date: 10 May 2025

